---
output: rmarkdown::github_document
---

# tazinhomiscellaneous

[![Travis-CI Build Status](https://travis-ci.org/Tazinho/tazinhomiscellaneous.svg?branch=master)](https://travis-ci.org/Tazinho/tazinhomiscellaneous) [![Coverage status](https://codecov.io/gh/Tazinho/tazinhomiscellaneous/branch/master/graph/badge.svg)](https://codecov.io/github/Tazinho/tazinhomiscellaneous?branch=master)

## Overview

Miscellaneous helper functions.

### Installation

```{r}
devtools::install_github("Tazinho/tazinhomiscellaneous", force = TRUE)
```

## `prepare_factors`

`prepare_factors` prepares character vectors for supervised machine learning. Rare levels in the training data are marked as rare in the whole dataset and levels that only occur in the test data are marked as new. Other packages that use this approach are the **vtreat** and the **recipes** pkg. However, in a very basic workflow, i.e. just using factor encoding, this might already suffice.

```{r, warning=FALSE, message=FALSE, collapse=TRUE}
library(tazinhomiscellaneous)
library(purrr)
library(dplyr)

train <- tibble(stay_same  = c('a','a','a','a','a','b','b','a','b','b','b', NA, NA),
                some_rare  = c('c','d','e','e','a','b','b','a','b','b','b', NA, NA),
                some_new   = c('c','d','e','e','a','b','b','a','b','b','b', NA, NA),
                only_new   = c('a','a','a','a','a','a','a','a','a','a','a','a','a'),
                integer    = c( 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L,10L,11L,12L,13L),
                logical    = c(  T,  F,  T,  F,  T,  F,  T,  F,  T,  F,  T,  F,  T))
test  <- tibble(stay_same  = c('a','a','a','a','a','b','b','a','b','b','b', NA, NA),
                some_rare  = c('c','c','c','c','c','d','b','a','b','b','b', NA, NA),
                some_new   = c('f','a','a','g','a','b','b','a','b','b','b', NA, NA),
                only_new   = c('b','b','b','b','b','b','b','b','b','b','b','b','b'),
                integer    = c( 1L, 2L, 3L, 4L, 5L, 6L, 7L, 8L, 9L,10L,11L,12L,13L),
                logical    = c(  T,  F,  T,  F,  T,  F,  T,  F,  T,  F,  T,  F,  T))

train_test <- bind_rows(train, test)

i_train <- 1:nrow(train)

train_test %>% 
  map_if(is.character, ~ prepare_factors(.x[i_train], .x[-i_train], output_type = "character")) %>% 
  as_tibble() %>% print(n = nrow(.))

train_test %>% 
  map_if(is.character, ~ prepare_factors(.x[i_train], .x[-i_train], output_type = "integer")) %>% 
  as_tibble() %>% print(n = nrow(.))
```
